DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-04 paper/background.tex
..
Initial commit

To solve the problem of autonomous driving, a standard approach has
been decomposing the problem into multiple sub-problems,
such as lane marking detection, path planning, and low-level
control, which together form a processing pipeline~\cite{Bojarski2016}.
Recently, researchers are exploring another approach that dramatically
simplifies the standard control pipeline by applying deep neural
networks to directly produce control outputs from sensor
inputs~\cite{Levine2016}. Figure~\ref{fig:end-to-end-control}
shows the differences between the two approaches.

\begin{figure}[h]
  \centering
  \includegraphics[width=.75\textwidth]{figs/endtoend_redrawn}
  \caption{Standard robotics control vs. DNN based end-to-end
    control. Adopted from ~\cite{Levine2017cs294}.}
  \label{fig:end-to-end-control}
\end{figure}

The use of neural networks for end-to-end control of autonomous
car was first demonstrated in the late 1980s~\cite{Pomerleau1989},
using a small 3-layer fully connected neural network; and subsequently
in a DARPA Autonomous Vehicle (DAVE) project in early
2000s~\cite{LeCun:04}, using a 6 layer convolutional neural network
(CNN); and most recently in NVIDIA's DAVE-2
project~\cite{Bojarski2016}, using a 9 layer CNN. In all of these projects,
the neural network models take raw image pixels as input and directly
produce steering control commands, bypassing all intermediary steps and
hand-written rules used in the conventional robotics control approach.  
NVIDIA's latest effort reports that their trained CNN
autonomously controls their modified cars on public roads without human
intervention~\cite{Bojarski2016}.

Using deep neural networks involves two distinct
phases~\cite{NVIDIA2015}. The first
phase is \emph{training} during which the weights of the network are
incrementally updated by backpropagating errors it sees from the
training examples. Once the network is trained---i.e., the weights of
the network minimize errors in the training examples---the next phase
is \emph{inferencing}, during which unseen data is fed to the network
as input to produce predicted output (e.g., predicted image
classification). In general, the training phase is more computationally
intensive and requires high throughput, which is generally not
available on embedded platforms. The inferencing phase, on the
other hand, is relatively less computationally intensive and latency becomes
as important, if not moreso, as computational throughput, because many
use-cases have strict real-time requirements (e.g., search query
latency).

@@

Accelerating AI workloads, especially inferencing
operations, has received a lot of attention from academia and industry
in recent years as applications of deep learning are broadening to
areas of real-time embedded systems such as autonomous vehicles. These
efforts include the development of various heterogeneous architecture-based 
system-on-a-chips (SoCs) that may include multiple cores, GPU,
DSP, FPGA, and neural network optimized ASIC hardware~\cite{Jouppi2017}.
Consolidating multiple tasks on SoCs with lots of shared hardware
resources while guaranteeing real-time performance is also an active
research area, which is orthogonal to improving raw
performance. Consolidation is necessary for efficiency, but unmanaged 
interference can nullify the benefits of consolidation~\cite{Kim2016}.
For these reasons, finding a good computing platform is a
non-trivial task, one that requires a deep understanding of the
workloads and the hardware platform being utilized.

The \emph{primary objectives of this study} are to understand (1) the
necessary computing performance for applying AI technology-based
robotics systems, and (2) what kind of computing architecture and
runtime supports are most appropriate for such workload. To
achieve these goals, we implement a low-cost autonomous car platform
as a case-study and systematically conduct experiments, which we will 
describe in the subsequent sections.

>>>>

To solve the problem of autonomous driving, a standard approach has
been decomposing the problem into multiple sub-problems,
such as lane marking detection, path planning, and low-level
control, which together form a processing pipeline~\cite{Bojarski2016}.
Recently, researchers have begun exploring another approach that dramatically
simplifies the standard control pipeline by applying deep neural
networks to directly produce control outputs from sensor
inputs~\cite{Levine2016}. Figure~\ref{fig:end-to-end-control}
shows the differences between the two approaches.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/endtoend_redrawn}
  \caption{Standard robotics control vs. DNN based end-to-end
    control. Adopted from ~\cite{Levine2017cs294}.}
  \label{fig:end-to-end-control}
\end{figure}

The use of neural networks for end-to-end control of autonomous
cars was first demonstrated in the late 1980s~\cite{Pomerleau1989},
using a small 3-layer fully connected neural network; and subsequently
in a DARPA Autonomous Vehicle (DAVE) project in early
2000s~\cite{LeCun:04}, using a 6 layer convolutional neural network
(CNN); and most recently in NVIDIA's DAVE-2
project~\cite{Bojarski2016}, using a 9 layer CNN. In all of these projects,
the neural network models take raw image pixels as input and directly
produce steering control commands, bypassing all intermediary steps and
hand-written rules used in the conventional robotics control approach.  
NVIDIA's latest effort reports that their trained CNN
autonomously controls their modified cars on public roads without human
intervention~\cite{Bojarski2016}.

Using deep neural networks involves two distinct
phases~\cite{NVIDIA2015}. The first
phase is \emph{training} during which the weights of the network are
incrementally updated by backpropagating errors it sees from the
training examples. Once the network is trained---i.e., the weights of
the network minimize errors in the training examples---the next phase
is \emph{inferencing}, during which unseen data is fed to the network
as input to produce predicted output (e.g., predicted image
classification). In general, the training phase is more computationally
intensive and requires high throughput, which is generally not
available on embedded platforms. The inferencing phase, on the
other hand, is relatively less computationally intensive and latency becomes
as important, if not moreso, as computational throughput, because many
use cases have strict real-time requirements (e.g., search query
latency).

@@

Accelerating AI workloads, especially inferencing
operations, has received a lot of attention from academia and industry
in recent years as applications of deep learning are broadening to include
areas of real-time embedded systems such as autonomous vehicles. These
efforts include the development of various heterogeneous architecture-based 
system-on-a-chips (SoCs) that may include multiple cores, GPU,
DSP, FPGA, and neural network optimized ASIC hardware~\cite{Jouppi2017}.
Consolidating multiple tasks on SoCs with a lot of shared hardware
resources while guaranteeing real-time performance is also an active
research area, which is orthogonal to improving raw
performance. Consolidation is necessary for efficiency, but unmanaged 
interference can nullify the benefits of consolidation~\cite{Kim2016}.
For these reasons, finding a good computing platform is a
non-trivial task, one that requires a deep understanding of the
workloads and the hardware platform being utilized.

The \emph{primary objectives of this study} are to understand (1) the
necessary computing performance for applying AI technology-based
robotics systems, and (2) what kind of computing architecture and
runtime supports are most appropriate for such a workload. To
achieve these goals, we implement a low-cost autonomous car platform
as a case-study and systematically conduct experiments, which we will 
describe in the subsequent sections.

### 2018-04-04 paper/comparison.tex
Initial commit

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/compare_core}
  \caption{Average control loop execution time.} 
  \label{fig:sys_core}
\end{figure}

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used.
First, both the Intel UP and Jetson TX2 exhibit superior performance when
compared with the Raspberry Pi 3. 
When all four CPU cores are used, the Intel UP is 1.33X faster than
the Pi 3, while the TX2 (CPU) and TX2 (GPU) are 2.79X and 4.16X times faster,
respectively, than the Pi 3. 
As a result, they are all able to satisfy the 33.$\overline{\mbox{33}}$ ms 
WCET by a clear margin,
%%  (in the worst case, the UP Board would 
%% still meet it by $\sim$20 ms) --> where's the data showing this?
and, in the case of the TX2, 50 Hz or even 100 Hz real-time control is
feasible with the help of its GPU. Another observation is that the TX2
(GPU) performance does not change much, as most of the neural network 
computation is done at the GPU.

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/compare_model}
  \caption{Average control loop execution time when multiple DNN
    models are co-scheduled. }
  \label{fig:sys_model}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/compare_benchmark}
  \caption{Average control loop execution time in the presence of an
    increasing number of memory intensive applications on idle CPU cores.}
  \label{fig:sys_bench}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/compare_l2missrate}
  \caption{L2 miss rates in the presence of an increasing number of 
			memory intensive applications on idle CPU cores.}
  \label{fig:sys_l2miss}
\end{figure}

Finally, we compare the effect of co-scheduling memory bandwidth
intensive synthetic benchmarks on the DNN control loop timing.

Figure~\ref{fig:sys_bench} shows the results. As discussed in 
Section~\ref{sec:eval-memhog}, we observed dramatic execution time
increases, up to 11.6X, in Raspberry Pi 3 as we increased the number of
co-scheduled tasks. We also observe increased control loop execution
timing in the Intel Up and Jetson TX2, but the degree of the increase is 
not as dramatic as the Pi 3. Compared to their respective solo timings 
(i.e., the model runs on a single core in isolation), Intel UP suffers up to
2.3X execution time increase; TX2 (CPU) and TX2 (GPU) suffer up to
2.2X and 2.1X increases, respectively. This is somewhat surprising
because the Raspberry Pi 3's cores are in-order architecture based while
the cores in the Intel Up and NVIDIA TX2 are out-of-order architecture
based, and that the memory intensive tasks on out-of-order cores can
generate more memory traffic. We believe that this is because the
memory subsystems in the Intel UP and TX2 platforms provide higher
performance than the memory subsystem of the Pi 3 as suggested from
the measured memory bandwidth results in Table~\ref{tbl:platforms}
('Measured Bandwidth').

@@

Figure~\ref{fig:sys_l2miss} shows the L2 miss rates of DNN control
loop. The key takeaway of this result is that the L2 miss rate is a
poor indicator to the execution time of the control loop. As shown
already, the Raspberry Pi 3's increased L2 misses do not fully explain
increases in processing times. In case of the Intel UP, as the number of
interfering Bandwidth benchmark instances increases, the L2 miss rates
even drop slightly. In case of the TX2 (CPU), from solo to one co-runner,
L2 miss rate increase almost twice, but then the execution time
increase is a little less than 10\%. However, when there are
co-runners, even though the L2 miss rates are largely unchanged, the
DNN processing time increases significantly. The TX2 (GPU) also shows
similar behavior. All of these results essentially point to the fact
that DNN inferencing workload is largely memory performance sensitive
but not L2 cache space sensitive.

@@

In summary, we find that today's embedded computing platforms, even as
inexpensive as a Raspberry Pi 3, are powerful enough to support
vision and end-to-end deep learning based real-time control
applications. Furthermore, availability of CPU cores and GPU on these
platforms allow consolidating mutiple deep neural network based AI
workloads. However, shared resource contention among these diverse
computing resources remains an important issue that must be understood
and controlled, especially for safety-critical applications.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_core}
  \caption{Average control loop execution time.} 
  \label{fig:sys_core}
\end{figure}

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used.
First, both the Intel UP and Jetson TX2 exhibit superior performance when
compared with the Raspberry Pi 3. 
When all four CPU cores are used, the Intel UP is 1.33X faster than
the Pi 3, while the TX2 (CPU) and TX2 (GPU) are 2.79X and 4.16X times faster,
respectively, than the Pi 3. 
As a result, they are all able to satisfy the 33.$\overline{\mbox{33}}$ ms 
WCET by a clear margin,
%%  (in the worst case, the UP Board would 
%% still meet it by $\sim$20 ms) --> where's the data showing this?
and, in the case of the TX2, 50 Hz or even 100 Hz real-time control is
feasible with the help of its GPU. Another observation is that the TX2
(GPU) performance does not change much, as most of the neural network 
computation is done by the GPU.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_model}
  \caption{Average control loop execution time when multiple DNN
    models are co-scheduled. }
  \label{fig:sys_model}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_benchmark}
  \caption{Average control loop execution time in the presence of an
    increasing number of memory intensive applications on idle CPU cores.}
  \label{fig:sys_bench}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_l2missrate}
  \caption{L2 miss rates in the presence of an increasing number of 
			memory intensive applications on idle CPU cores.}
  \label{fig:sys_l2miss}
\end{figure}

Finally, we compare the effect of co-scheduling memory bandwidth
intensive synthetic benchmarks on the DNN control loop timing. 
Figure~\ref{fig:sys_bench} shows the results. As discussed in 
Section~\ref{sec:eval-memhog}, we observed dramatic execution time
increases, up to 11.6X, in Raspberry Pi 3 as we increased the number of
co-scheduled tasks. We also observe increased control loop execution
timing in the Intel Up and Jetson TX2, but the degree of the increase is 
not as dramatic as the Pi 3. Compared to their respective solo timings 
(i.e., the model runs on a single core in isolation), Intel UP suffers up to
2.3X execution time increase; TX2 (CPU) and TX2 (GPU) suffer up to
2.2X and 2.1X increases, respectively. This is somewhat surprising
because the Raspberry Pi 3's cores are in-order architecture based while
the cores in the Intel Up and NVIDIA TX2 are out-of-order architecture
based, and that the memory intensive tasks on out-of-order cores can
generate more memory traffic. We believe that this is because the
memory subsystems in the Intel UP and TX2 platforms provide higher
performance than the memory subsystem of the Pi 3 as suggested from
the measured memory bandwidth results in Table~\ref{tbl:platforms}
('Measured Bandwidth').

@@

Figure~\ref{fig:sys_l2miss} shows the L2 miss rates of DNN control
loop. The key takeaway of this result is that the L2 miss rate is a
poor indicator to the execution time of the control loop. As shown
already, the Raspberry Pi 3's increased L2 misses do not fully explain
increases in processing times. In case of the Intel UP, as the number of
interfering Bandwidth benchmark instances increases, the L2 miss rates
drop slightly. In the case of the TX2 (CPU), from solo to one co-runner,
L2 miss rates almost double, but then the execution time
increase is a little less than 10\%. However, when there are
co-runners, even though the L2 miss rates are largely unchanged, the
DNN processing time increases significantly. The TX2 (GPU) also shows
similar behavior. All of these results essentially point to the fact
that DNN inferencing workload is largely memory performance sensitive
but not L2 cache space sensitive.

@@

In summary, we find that todays embedded computing platforms, even as
inexpensive as a Raspberry Pi 3, are powerful enough to support
vision and end-to-end deep learning based real-time control
applications. Furthermore, availability of CPU cores and GPU on these
platforms allow consolidating mutiple deep neural network based AI
workloads. However, shared resource contention among these diverse
computing resources remains an important issue that must be understood
and controlled, especially for safety-critical applications.

### 2018-04-04 paper/evaluation-cachepart.tex
Initial commit

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth]{figs/cache-mapping}
  \caption{A memory mapping of the cache sets for the Broadcom 
BCM2837 processor used in the Raspberry Pi 3 Model B.}
  \label{fig:cache-mapping}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/palloc_multicore}
  \caption{Average control loop execution time vs.  % of L2 cache
    L2 cache partition size.}
  \label{fig:palloc_multicore}
\end{figure}

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.7\textwidth]{figs/palloc_multimodel}
%%   \caption{Timing impact of co-scheduling multiple DNNs when cache 
%% partitioning is enabled.}
%%   \label{fig:palloc_multimodel}
%% \end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=.7\textwidth]{figs/palloc_bandwidth_exectime}
  \caption{Timing impact of co-scheduling memory intensive co-runners 
when cache partitioning is enabled.}
  \label{fig:palloc_bandwidth_exectime}
\end{figure}

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.7\textwidth]{figs/palloc_bandwidth_bus}
%%   \caption{Bus access impact of co-scheduling memory intensive co-runners 
%% when cache partitioning is enabled.}
%%   \label{fig:palloc_bandwidth_bus}
%% \end{figure}

@@

In the first experiment, we investigate the cache space sensitivity of
the DeepPicar's DNN-based control loop. Using PALLOC, we create 4
different cgroups which are configured to use 2, 4,
6, 8 colors (25\%, 50\%, 75\%, 100\% of the L2 cache
space, respectively). We then execute the control loop on each cache
partition (cgroup) and measure the average processing time.

If performance improves as a result of partitioning the shared cache 
then we know that the DNN, to some extent, relies on shared cache 
performance in addition to shared DRAM performance. On the other 
hand, if there is no improvement in performance, then it can be 
observed that the shared memory is more critical to the performance 
of the DNN.

We run the DNN model with different amounts of L2 cache being
available based on the number of colors being used. For example, if two 
colors are used, then 25\% of the L2 cache is available, whereas if all 
8 colors are used, 100\% of the L2 cache is available. Particularly, we 
test the performance of the model when it utilizes a single core and
all four of the available cores. The results can be seen in 
\ref{fig:palloc_multicore}. As expected, the amount of L2 cache 
available to the model does not result in any significant changes in 
performance. This can also be seen by the L2 miss rates of the model 
seen in \ref{fig:palloc_multicore_l2missrate}. As more cache space 
becomes avaiable, the percentage of L2 misses decreases, which doesn't 
affect the real-time performance of the DNN. As such, we find that a 
single model is not sensitive to the shared L2 cache.

We also co-schedule multiple models to see how cache partitioning affects
interference between them. Each model uses an equal number of colors, and
are thus given equal amounts of L2 cache space, and there is no overlap
in the colors used, so no L2 cache is shared between models. As can be 
seen in \ref{fig:palloc_multimodel}, the performance of the models 
remains the same as when no cache partitioning was employed. Based of 
these results, we find that contention for the L2 cache is not the main
source of interference between multiple DNN models.

Finally, we run a single model alongside memory intensive co-runners 
again, but ensure that each task is given equal amounts of L2 cache space.
For this, we assign two colors to each task, regardless of the number of
tasks being scheduled. As a result, the entire cache is not utilized in
experiments with less than four tasks. The results can be seen in Figure
\ref{fig:palloc_bandwidth_exectime}. With zero or one co-runners, the DNN
performance doesnt't change relative to when the cache wasn't partitioned.
However, we find that with two or more co-runners, DNN performance becomes
worse. In the case of two co-runners, average control loop time increases
by 66.31 ms, or 26\%, and with three co-runners, the average time
is 265.64 ms, of 49\%, greater.
At the same time, though, the L2 miss rates of the model don't correlate 
to the timing increases seen, as is shown in 
\ref{fig:palloc_bandwidth_l2missrate}. Instead, we find that the number
of bus accesses increases when cache partitions are used, and they mirror
the timing increases of the model. This can be seen in Figure 
\ref{fig:palloc_bandwidth_bus}. These additional bus accesses are
most likely caused by the L2 prefetcher, as it can generate additional bus
accesses that aren't counted as L2 misses. As a result, we find that cache
partitioning is detrimental to the performance of the DNN so long as the 
L2 prefetcher is enabled (we have not yet found a way to disable it on
the Pi 3). Furthermore, no cache sensitivity was displayed by the model,
thus showing that the performance of the L2 cache is not vital for DNN 
performance when co-runners are introduced.

By partitioning the shared L2 cache, we find that no noticable 
improvements are gained and that performance remains consistent, or 
decreases, depending on the circumstances. In all experiements, the DNN
shows no sensitivity to the shared L2 cache. As a result, we conclude 
that cache partitioning is not an effective isolation mechanism, and that 
the performance of the shared DRAM controller is of greater importance 
to the real-time efficiacy of the DeepPicar.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=.5\textwidth]{figs/cache-mapping}
  \caption{A memory mapping of the cache sets for the Broadcom 
BCM2837 processor used in the Raspberry Pi 3 Model B.}
  \label{fig:cache-mapping}
\end{figure}

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.7\textwidth]{figs/palloc_bandwidth_modelbus}
%%   \caption{Model bus access impact of co-scheduling memory intensive co-runners 
%% when cache partitioning is enabled.}
%%   \label{fig:palloc_bandwidth_modelbus}
%% \end{figure}

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.7\textwidth]{figs/palloc_bandwidth_bus}
%%   \caption{Total bus access impact of co-scheduling memory intensive co-runners 
%% when cache partitioning is enabled.}
%%   \label{fig:palloc_bandwidth_bus}
%% \end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/palloc_multicore}
  \caption{Average control loop execution time vs.  % of L2 cache
    L2 cache partition size.}
  \label{fig:palloc_multicore}
\end{figure}

In the first experiment, we investigate the cache space sensitivity of
the DeepPicar's DNN-based control loop. Using PALLOC, we create 4
different cgroups which are configured to use 2, 4,
6, and 8 colors (25\%, 50\%, 75\%, and 100\% of the L2 cache
space, respectively). We then execute the control loop on each cache
partition (cgroup) and measure the average processing time.

If performance improves as a result of partitioning the shared cache 
then we know that the DNN, to some extent, relies on shared cache 
performance in addition to shared DRAM performance. On the other 
hand, if there is no improvement in performance, then it can be 
observed that the shared memory is more critical to the performance 
of the DNN.
%% We run the DNN model with different amounts of L2 cache being
%% available based on the number of colors being used. For example, if two 
%% colors are used, then 25\% of the L2 cache is available, whereas if all 
%% 8 colors are used, 100\% of the L2 cache is available. Particularly, we 
%% test the performance of the model when it utilizes a single core and
%% all four of the available cores. 
The results can be seen in 
\ref{fig:palloc_multicore}. As expected, the amount of L2 cache 
available to the model does not result in any significant changes in 
performance. 
%% This can also be seen by the L2 miss rates of the model 
%% seen in \ref{fig:palloc_multicore_l2missrate}. As more cache space 
%% becomes avaiable, the percentage of L2 misses decreases, which doesn't 
%% affect the real-time performance of the DNN. As such, we find that a 
%% single model is not sensitive to the shared L2 cache.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/palloc_multimodel}
  \caption{Timing impact of co-scheduling multiple DNNs when cache 
partitioning is enabled.}
  \label{fig:palloc_multimodel}
\end{figure}

We also co-schedule multiple models to see how cache partitioning affects
interference between them. Each model uses an equal number of colors, and
are thus given equal amounts of L2 cache space, and there is no overlap
in the colors used, so no L2 cache is shared between models. As can be 
seen in Figure \ref{fig:palloc_multimodel}, the performance of the models 
remains the same as when no cache partitioning was employed. Based of 
these results, we find that contention for the L2 cache is not the main
source of interference between multiple DNN models.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/palloc_bandwidth_exectime}
  \caption{Timing impact of co-scheduling memory intensive co-runners 
when cache partitioning is enabled.}
  \label{fig:palloc_bandwidth_exectime}
\end{figure}

Finally, we run a single model alongside memory intensive co-runners 
again, but ensure that each task is given equal amounts of L2 cache space.
For this, we assign two colors to each task, regardless of the number of
tasks being scheduled. As a result, the entire cache is not utilized in
experiments with less than four tasks. The results can be seen in Figure
\ref{fig:palloc_bandwidth_exectime}. When the model runs by itself, performance
is slightly worse due to less cache space being available (this was also seen in 
Figure \ref{fig:palloc_multicore}). With one or two co-runners, the DNN
performance doesnt't change relative to when the cache wasn't partitioned.
When three co-runners are present, DNN performance becomes slightly
better, with a improvement of \textasciitilde6.5\%. However, as the 
performance improvement is minimal, we do not believe that cache 
partitioning is effective for protecting the model from interference from
other memory intensive processes.
%% At the same time, though, the L2 miss rates of the model don't correlate 
%% to the timing increases seen, as is shown in 
%% \ref{fig:palloc_bandwidth_l2missrate}. Instead, we find that the number
%% of bus accesses increases when cache partitions are used, and they mirror
%% the timing increases of the model. This can be seen in Figure 
%% \ref{fig:palloc_bandwidth_bus}. These additional bus accesses are
%% most likely caused by the L2 prefetcher, as it can generate additional bus
%% accesses that aren't counted as L2 misses. As a result, we find that cache
%% partitioning is detrimental to the performance of the DNN so long as the 
%% 0L2 prefetcher is enabled (we have not yet found a way to disable it on
%% the Pi 3). Furthermore, no cache sensitivity was displayed by the model,
%% thus showing that the performance of the L2 cache is not vital for DNN 
%% performance when co-runners are introduced.

By partitioning the shared L2 cache, we find that no noticable 
improvements are gained and that performance remains consistent, or 
slightly decreases, depending on the circumstances. In all experiements,
the DNN shows no sensitivity to the shared L2 cache. As a result, we 
conclude that cache partitioning is not an effective isolation mechanism, 
and that the performance of the shared DRAM controller is of greater 
importance to the real-time efficiacy of the DeepPicar.
